### 2019-02-14 sections/intuition.tex
Changes to section 3.4

\subsection{Tasks can be observed for their current status at all time}

\fixme{Extend}
The value of a task can be present or not.

Because every task has an observable value of a specified type,
it is always possible to generate a (graphical) user interface from a \TOPHAT specification.
%NOTE: depends on: editors
The structure of the specification prescribes the structure of the \UI and possible input events.
Editors form the leaves of such trees \todo{which trees?}.

>>>>

\subsection{Tasks can be observed}

Several oberservations can be made of a task. The most obvious and basic
observation is determining the value of a task. Not all tasks have a value
though, for example, the empty editor $\Enter \tau$ does not have a value.

We can also observe what potential events a task can take. This is essential in
generating a (graphical) user interface for tasks. For example, the task
$\Edit 5$ can take a new value as input, or it can be cleared, resulting in an
empty editor of type Int.

In order to complete the user interface, we also need to be able to render a
task. This is done in a modular and recursive fashion. Every combinator renders
their sub-tasks in a certain way. For example, when rendering a task that is
composed of a step combinator, we simply render the left side of it.

When we are able to render tasks, and we are able to list all possible inputs,
we can obviously construct a user interface, that displays the current state of
the system, together with buttons that show the potential actions a user can
apply.

Another useful observation is to determine whether a task results in $\Fail$.
This is used by the step combinator, as demonstrated in
Example~\ref{Vending machine}, and the choice combinator, to prevent users from
picking a task that fails.
